PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$

### 2015-03-11 qfenv_paper/ApJ submission/qf_environment.tex
Title change
minor changes

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}

@@

them. However, in the recent Universe a substantial fraction of the

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.eps, height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig4.eps, height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
          galaxies in low (left) and high (right) density
          environments for $z < 0.8$. $f_{\mathrm{Q}}$s were calculated
          using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}. Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
    \end{center}
\end{figure*}

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig5, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial
          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
          high (red) density environments within the redshift range $z
          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
          \mathcal{M}_\odot$ (solid fill) and $10^{11}
          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
          the best-fit parameter $b$ in Equation \ref{eq:qffit}
          represented by the width of the line. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

@@

\def \iovinopanel {b}
\def \kovacpanel {b}
\def \pengpanel {c}
\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig6.eps, height=\textwidth, angle=90}
        \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel). The $f_{\mathrm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works. High density environment is represented in red and low density environment is represented in blue. The $f_{\mathrm{Q}}$ value from \cite{geha12a} is the $f_{\mathrm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. Uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\mathrm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\mathrm{Q}}$ estimates. We also plot the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure*}

>>>>

\title{PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}

@@

them. In other words, in the recent Universe a substantial fraction of the

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.pdf, height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig4.pdf, height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
          galaxies in low (left) and high (right) density
          environments for $z < 0.8$. $f_{\mathrm{Q}}$s were calculated
          using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}. Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
    \end{center}
\end{figure*}

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig5.pdf, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial
          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
          high (red) density environments within the redshift range $z
          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
          \mathcal{M}_\odot$ (solid fill) and $10^{11}
          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
          the best-fit parameter $b$ in Equation \ref{eq:qffit}
          represented by the width of the line. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

@@

\def \iovinopanel {b}
\def \kovacpanel {b}
\def \pengpanel {c}
\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig6.pdf, height=\textwidth, angle=90}
        \caption{$f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}=10^{10.5} \mathcal{M}_\odot)$ evolution compared to $f_{\mathrm{red}}(\mathcal{M}_{*} \sim 10^{10.5} \; \mathcal{M}_{\odot})$ in the literature: \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross) from SDSS (panel a), \cite{Iovino:2010aa} (empty square) and \cite{Kovac:2014aa} (triangle) from zCOSMOS (panel \kovacpanel), and \cite{Peng:2010aa} from both SDSS and zCOSMOS (panel \pengpanel). The $f_{\mathrm{red}}$ values from \cite{Iovino:2010aa}, \cite{Kovac:2014aa}, \cite{Baldry:2006aa}, and \cite{Peng:2010aa} are calculated from the best-fit parameterizations presented in the respective works. High density environment is represented in red and low density environment is represented in blue. The $f_{\mathrm{Q}}$ value from \cite{geha12a} is the $f_{\mathrm{Q}}$ value at $\mathcal{M} = 10^{10.55} \mathcal{M}_{\odot}$. Uncertainties in the \cite{Iovino:2010aa} best-fit $f_{\mathrm{red}}$ is omitted due to insufficient information on the cross correlation terms of the fit parameters. For \cite{Kovac:2014aa} we apply the offset between the color-based and SFR-based galaxy classification in order to plot the $f_{\mathrm{Q}}$ estimates. We also plot the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution of our sample with varying environment cut-offs specified on the top right. As in Figure \ref{fig:qffit} the width of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}} = 10^{10.5} \mathcal{M}_\odot)$ evolution represent the uncertainty in the best-fit parameters of Equation \ref{eq:qffit}.}         \label{fig:qffit_comp}
    \end{center}
\end{figure*}
